\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{hyperref}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{Okan UYSAL}}\\
	Istanbul(Asia), TURKEY
	\vspace{0.04cm}
	\\
	\raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  \href{tel:+905078873913}{+90 (507) 887-3913} \hfill\raisebox{-0.2\height}{\Large \faEnvelopeSquare} \ \ \href{mailto:uysal.okan.2010@gmail.com}{uysal.okan.2010@gmail.com} \hfill \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ \href{https://www.github.com/OkanUysal}{github.com/OkanUysal} 
	\\
	\raisebox{-0.2\height}{\Large \faLinkedinSquare} \ \ \href{https://www.linkedin.com/in/okanuysal}{linkedin/in/okanuysal} \raisebox{-0.2\height}{\Large \faGlobe} \ \ \href{https://okanuysal.com}{okanuysal.com}
\end{center}


\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{TÜBİTAK}}
	      {\textbf{Istanbul(Asia), TURKEY}}
	      \headerrow
	      {\emph{Senior Software Engineer}}
	      {\emph{January 2022 -- Present}}
	      \begin{itemize*}
	      	\item Working as a test automation team leader and project system engineer.
	      	\item Working as an integration manager in the project.
	      	\item Taking part in the designs of the CI in the project. Designs were created in test automation tools and infrastructure libraries were written.
	      \end{itemize*}

	\item
	      \headerrow
	      {\textbf{TÜBİTAK}}
	      {\textbf{Istanbul(Asia), TURKEY}}
	      \headerrow
	      {\emph{Senior Software Engineer}}
	      {\emph{October 2020 -- January 2022}}
	      \begin{itemize*}
	      	\item Leading a 7-person RTOS core team. As the core team, memory, communaction, scheduler, process/thread, smp ect. topics are being developed.
	      	\item Taking part in road map determination and design studies in the project.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{HUAWEI}}
	      {\textbf{Istanbul, TURKEY}}
	      \headerrow
	      {\emph{Full Stack Developer}}
	      {\emph{June 2020 -- Agust 2020}}
	      \begin{itemize*}
			\item Working as a system engineer and full stack developer in the project. Many components such as captcha and media player were developed in the e-interview project.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{TÜBİTAK}}
	      {\textbf{Istanbul(Asia), TURKEY}}
	      \headerrow
	      {\emph{Software Engineer, RTOS Core Developer}}
	      {\emph{September 2019 -- May 2020}}
	      \begin{itemize*}
	      	\item Improved clock/timer package. CPU usage has been reduced from 30% to 5% in the number of max timers.
	      	\item Design studies were carried out in the code tree of the project. Fixed unnecessary code snippets in profiles.
	      \end{itemize*}
	      \headerrow
	      {\emph{Software Engineer, Test Automation Developer}}
	      {\emph{December 2015 -- September 2019}}
	      \begin{itemize*}
	      	\item Developed full automatic tool for RTOS. This tool provided commination between host and target. So all written tests are run on the device and the results are reported in excel and html.
	      	\item Developed many unit tests and helped improve the quality of the product. Static analysis and dynamic analysis tools were integrated into the project within the scope of DO-178 Level A. LDRA was used as the tool.
	      \end{itemize*}
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Languages:}
	      C, Java, Bash Script, Python.
	\item \textbf{Software:}
	      Git, Clearcase, LibGDX, Gradle, Spring Boot, Java SWT, Firebase, Selenium.
	\item \textbf{Tools:}
	      Eclipse, Android Studio, VS Code, WireShark, Github, Gitlab.
	\item \textbf{Certificates:}
	      ISO-26262 Functional Safety -TUV Nord, 1.National Blockchain Workshop - TÜBİTAK BİLGEM, ARM Cortex-R4 Software Design - Doulos, Intel x86 Assembly Language and Architecture - MindShare, Coursera Standford Algorithms, Coursera Google Foundations of Project Management.
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{Hacettepe University}}
	      {\textbf{Ankara, TURKEY}}
	      \headerrow
	      {\emph{B.S. Computer Science} (\textbf{GPA:} 2.78/4.00)}
	      {\emph{September 2010 -- August 2015}}
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Interest}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Sport:}
	      Table tennis, Running, Hiking, Skiing, Swimming.
	\item \textbf{E-Sport:}
	      Watch E-Sport, Play PC Games
	\item \textbf{Develop Mobile Apps:}
	      Educational Apps, Strategy Games, Finance Apps, Data mining.
\end{itemize}

\end{document}
